---
title: "HW 1"
date: 'Due: Thursday January 18, 2pm'
output:
  pdf_document: default
---

#### Instructions
* Produce your assignment as a RMarkdown document
  rendered to pdf (knit to pdf).
* Also submit your Rmd file (it will not be graded but we want it for reference purposes).
* Show all the code (use `echo=TRUE` as option in R chunks) as
well as the results.
* 10 points per exercise.
* See Syllabus for HW policies.

#### Data for exercises:
```{r}
data <- c(23, 89,  1, 34,
          26, 85, 24, 43,
          23, 93, 29, 45,
          32, 42, 43, NA,
          21, 54, 37, 76)
```

<br />

### Positive Integral Quantities Index Vector
* Values in the index vector must lie in the set 
{1, 2, ..., length(x)}.
* Values not in this set will produce NAs.
* Corresponding elements of the vector are selected and
  concatenated, in that order, in the result.
* The index vector can be of any length and the result
is of the same length as the index vector.

<br />

#### Exercise 1:
Extract the elements of `data` found in positions
8, 3, 7, and 5.

####Answer
```{r}
data[c(8,3,7,5)]
```
<br />

#### Exercise 2:
Random sample and simple random sample:

First search on the Internet which is the difference
between:

* simple random sample
* random sample
(keep in mind that sometimes people confuse both namings)

(Note: the difference should be related to sampling with or without replacement).

Generate both a simple random sample and a random sample
of size 10 from `data`.

Hint: look the help for of function `sample`.
Extracting directly from `data`, a simple random sample is:
```{r}
sample(data, 10)
sample(data, 10, TRUE)
```

However, for didactical purposes on index vectors,
I ask you to first generate
a random index vector, and use it to extract the
chosen elements from `data`.

####Answer
```{r}
data[sample(length(data), 10, TRUE)]
```
<br />

#### Exercise 3:
Systematic sample:
Get a systematic sample of size `n = 5` from `data`
by extracting each value that lies every `K = N/n` elements
(where `N` is the total number of elements in `data`).

Your first element needs to be randomly determined
as a number between 1 and K.

Note: Your result needs to be a vector containing
the 5 elements that are part of your systematic sample.

####Answer
```{r}
a <- sample(1:(length(data)/5),1)
data[seq(from = a, to = length(data), by = (length(data)/5))]
```


### Negative Integral Quantities Index Vector
* Negative values in the index vector specify the values
to be excluded.

<br />

#### Exercise 4:
Using negative indexes, obtain a sub-vector by removing
from `data` elements in positions 3, 7, and at the end
(the position at the end must be removed in a general way,
even for vectors with different sizes).

####Answer
```{r}
data[c(-3, -7, -length(data))]
```
<br />

#### Exercise 5:
`data` has an even number of elements. Devise a general
strategy to remove only the 2 elements found in the middle.

####Answer
```{r}
data[c(-length(data)/2,-(length(data)/2+1))]
```

<br />

#### Exercise 6:
Obtain a vector of the differences
(second - first, third - second, ...)
using negative indexes.

Note: function `diff` does exactly this. you
can use it to verify that the result of your
solution (has to be a *one liner*) is OK:
```{r}
diff(data)
```
####Answer
```{r}
data1 <- data[c(-1)]
data2 <- data[c(-length(data))]
c(data1-data2)
```

<br />

### Logical Index Vectors
* Index vector must be of the *same length* as the vector
  from which elements are to be selected.
* If the length of the index vector is less than the vector,
  the index vector will be recicled with perhaps unwanted
  results.
* Values corresponding to TRUE in the index vector are
  selected.
* Values corresponding to FALSE are omitted.

<br />

#### Exercise 7:
Write an R expression that will return the sum value
of 820 for the elements of `data`.

Note: using function `sum` directly yields
```{r}
sum(data)
```
as `NA`s are contagious. `sum` has the parameter
`na.rm` to remove `NA`s before performing the sum.
```{r}
sum(data, na.rm = TRUE)
```

Your solution cannot use `na.rm`, but instead
use logical indexes, and be general
(not only for this specific example).

####Anwer
```{r}
sum(data[!is.na(data)])
```

<br />

#### Exercise 8:

Write an R expression that will return the positions
of values 23 and 43 in `data`.

####Answer
```{r}
which(data == 23 | data == 43)
```
<br />

#### Exercise 9:
Verify the "Empirical rule", that states that when data
is drawn from a Normal distribution,

* about 68% of the data is in the interval
  `(mean(x) - sd(x), mean(x) + sd(x))`
* about 95% of the data is in the interval
  `(mean(x) - 2 * sd(x), mean(x) + 2 * sd(x))`
* about 99.7% of the data is in the interval
  `(mean(x) - 3 * sd(x), mean(x) + 3 * sd(x))`

Hint: use "x <- rnorm(n)" to randomly generate
      a sample of size n from a standard
      normal distribution.
        
Use n = 1000

####Answer
```{r}
x <- rnorm(1000)
length(which(x <= sd(x) & x >= -sd(x)))/length(x)
length(which(x <= 2 * sd(x) & x >= -2 * sd(x)))/length(x)
length(which(x <= 3 * sd(x) & x >= -3 * sd(x)))/length(x)
```