---
title: "HW2"
author: "Aaron"
date: "1/26/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Exercise1
```{r}
## Load the library
library(ggplot2)
## Activate the mpg data.frame provided by ggplot2
data(mpg)
## New versions of ggplot provide a tibble and have all character variables, while ## older were data frames and had factors. Transform manufacturer to factor
## to show how most data.frames treat character variables.
mpg <- as.data.frame(mpg)
mpg$manufacturer <- factor(mpg$manufacturer)
```

####1. Inspect the structure of mpg data.frame. Note the kind of data provided.
```{r}
str(mpg)
```

####2. Run the summary function to learn more about the variables.
```{r}
summary(mpg)
```
####3. Get a subset of the data.frame including all cars that are not ford nor audi.
```{r}
mpgsub <- subset.data.frame(mpg, manufacturer != "ford" & manufacturer != "audi")
```

####4. Determine if the manufacturer variable (that is a factor) in your subset has or not dropped the now removed manufacurers audi and ford.
```{r}
c("audi", "ford") %in% mpgsub$manufacturer
```

####5. Devise a strategy to assure that the above factor has dropped the levels that have no elements
```{r}
mpgsub$manufacturer <- droplevels(mpgsub$manufacturer)
levels(mpgsub$manufacturer)
```

####6. Further subset the data making sure that only front drive midsize cars model 2008 with at least 20 highway or city miles per gallon are included.
```{r}
mpgsub2 <- subset.data.frame(mpgsub, drv == "f" & class == "midsize" & year == 2008 & (hwy >= 20 | cty >= 20))
mpgsub2$manufacturer <- droplevels(mpgsub2$manufacturer)
mpgsub2
```

####7. Determine how many cars per manufacturer satisfy these constraints. Only show manufacturers with at least one vehicle.
```{r}
table(mpgsub2$manufacturer)
```

####8. Only show the manufacturer(s) with more cars (Note: your solution should also contemplate the possibility of a tie for the first place.)
```{r}
total <- table(mpg$manufacturer)
row.names(total)[which(total == max(total))]
```

###Exercise2
```{r}
set.seed(123)
r <- rnorm(1000)

plot(qnorm((1:(length(r)-1))/(length(r)-1)), sort(r[-which.max(r)]),main = "Q-Q Plot", xlab = "Normal Theoretical Quantile", ylab = "Sorted Data")
abline(a = 0, b = 1)
```

###Exercise3
```{r}
set.seed(123)
r <- rgamma(1000, shape = 1)

plot(qgamma((1:(length(r)-1))/(length(r)-1), shape = 1), sort(r[-which.max(r)]),main = "Q-Q Plot", xlab = "Normal Theoretical Quantile", ylab = "Sorted Data")
abline(a = 0, b = 1)
```

###Exercise4
```{r}
stem(faithful$eruptions)

hist(faithful$eruptions)
rug(faithful$eruptions)

boxplot(faithful$eruptions)

shapiro.test(faithful$eruptions)
ks.test(faithful$eruptions, pnorm)
```
Both p-values are much smaller than 0.5 so eruption is not normally distribution.

###Exercise5

```{r}
library(UsingR)
data(father.son)

lmfs <- lm(sheight ~ fheight, data = father.son)
slmfs <- summary(lmfs)
anlmfs <- anova(lmfs)
```

####1. Extract the coefficients of the regression line from lmfs, and add the regression line (in red) to the scatterplot. Hint: use function abline (see help)
```{r}
coefficients(lmfs)
plot(father.son$fheight, father.son$sheight)
abline(reg = lmfs,col = "red")
```
####2. Plot the father heights on x and the residuals in y. Add a horizontal line at 0.

```{r}
plot(father.son$fheight, lmfs$residuals, xlab = "fheight", ylab = "residuals")
abline(0,0, col = "red")
```

####3. Extract the fstatistic from slmfs and perform the calculation to obtain the p-value of the anova of the regression (i.e., the line that says: F-statistic: 361.2 on 1 and 1076 DF, p-value: < 2.2e-16. (Hint: use the function pf that gives you the cumulative probability of an F distribution).
```{r}
pf(slmfs$fstatistic["value"],slmfs$fstatistic["numdf"],slmfs$fstatistic["dendf"],lower.tail = F)
```

####4. Extract the p-value directly from anlmfs.
```{r}
anlmfs$Pr
```
