---
title: "Strings and regular expressions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```


```{r}
library(stringr)
```


```{r}
a <- "This sentence is a string. It is long."
b <- c(a, "Here there was another string.")
```

### Useful string functions from stringr

#### `str_length`
Returns the length of a string (in characters).

```{r}
str_length(b)
```

```{r}
## Using base R
nchar(b)
```


#### `str_sub`
Extract substrings from a character vector.

Usage:
```{r}
## str_sub(string, start = 1L, end = -1L)
```


Example:
```{r}
str_sub(a, 6, 13)
```

The corresponding Base R function is
```{r}
substr(a, 6, 13)
```

#### Exercise:
Using negative indexes, extract "long" from `a`.



#### Exercise:
Using one call to `str_sub`, extract both "sentence"
and "long" from `a`.




#### Replacement form

We first assign it to another variable, as it will
be modified.

```{r}
tmp <- a
```

```{r}
str_sub(tmp, 15, 32) <- "will be"
tmp
```



### `str_locate` 
Locate the position of the first occurence of a pattern
in a string.

Usage:
```{r}
## str_locate(string, pattern)
```

```{r}
str_locate(b, "another")
```


`pattern` is a regular expression.

For example, the following will match the first character
as . is has special meaning in the context of regular
expressions (it means match any character).
```{r}
str_locate(b, ".")
```

To avoid interpretation as a special character, use `fixed`.
```{r}
str_locate(b, fixed("."))
```

Alternatively, you can do:
```{r}
str_locate(b, "\\.")
```



```{r}
## str_locate_all
str_locate(b, "is")
## To locate *all* instances
str_locate_all(b, "is")
## Is it case sensitive?
str_locate(b, "Is")
## Yes
```


```{r}
## Make it insensitive
str_locate(b, fixed("iS", ignore_case = TRUE))
```

### Exercise:
`str_count` can be used to find out how many times a pattern
is matched. For example:
```{r}
str_count(a, "is")
```

Find an alternative strategy, using str_sub and str_locate_all, to
count how many times "is" appears in `a`.




### `str_split`
Split up a string into a variable number of pieces.

```{r}
## str_split(string, pattern, n = Inf)
```


```{r}
str_split(b, " is ")
```

### `str_replace`
Replace first occurrence of a matched pattern in a string.

Usage:
```{r}
## str_replace(string, pattern, replacement)
```


```{r}
## Value: character vector.
str_replace(b, " is ", " was ")
```

```{r}
## str_replace_all
str_replace_all(b, " is ", " was ")
```




## Regular expressions

Search R help for "regular expression"

```{r}
str_view_all(b, "is")
```



```{r}
str_view_all(b, "is|was")
```

```{r}
str_view_all(b, " (is|was) ")
```


```{r}
str_replace_all(b, " (is|was) ", " will be ")
```


```{r}
str_view_all(b, "\\b(is|was)\\b") # match empty string
```



```{r}
str_replace_all(b, "\\b(is|was)\\b", "will be")
```

```{r}
C <- paste0("Info with -- that can change")
```

```{r}
str_split(C, "-.*-")
str_split(C, "-.+-")
str_split(C, "-.?-")
```


```{r}
str_view_all(C, "-.*-")
str_view_all(C, "-.+-")
str_view_all(C, "-.?-")
```


#### Exercise:
How you should modify the regular expression if the
dashes are replaced by parentheses?

```{r}
D <- paste0("Info with ( separator ) that can change")
```



```{r}
d <- c("423-84-2836", "324-2342-345",
       "243-d5-1923", "423-364-3765")
str_view_all(d, "-.{2}-")
str_view_all(d, "-[0123456789]{2}-")
str_view_all(d, "-[0-9]{2}-")
str_view_all(d, "-[[:digit:]]{2}-")
str_view_all(d, "-([0-9]{2}|[0-9]{4})-")
str_view_all(d, "-[0-9]{2,4}-")
```

```{r}
str_subset(d, "-.{2}-")
```


```{r}
str_detect(d, "-.{2}-")
```

Note: str_detect can be useful in a filter condition.

#### Exercise:
Get a subset from `mpg` where model contains the words
"pickup" and "2wd" or "4wd".




#### Exercise
Interpret what the following regular expression matches.
```{r}
# "^(1[0-2]|0[1-9])(\\.|/)(3[0-1]|[1-2][0-9]|0[1-9])(\\.|/)([0-9]{2,4})$"
```





```{r}
C <- paste0("Info with -sepasgfhsgdhgfdhrator- that can change")
```

```{r}
str_replace(C, "^.*-(.*)-.*$", "\\1")

str_replace(d, "^.*-(.+)-(.*)$", "\\2-hello-\\1")
```


```{r}
strings <- c("Home: 219 733.8965.  Work: 229-293-8753 ",
             "Home: 119 733.8965.  Work: 229-293-8753 ",
             "banana pear apple",
             "595 794 7569 / 387 287 6718")
phone <- "([2-9][0-9]{2})[- .]([0-9]{3})[- .]([0-9]{4})"

str_extract(strings, phone)
str_extract_all(strings, phone)

str_match(strings, phone)
str_match_all(strings, phone)
```


```{r}
email <- readRDS('data/email.rds')
str(email)
email[1]

cat(email[1])

breaks <- str_locate(email[1], "\n\n")
str(breaks)

header <- str_sub(email[1], end = breaks[,"start"])
body <- str_sub(email[1], start = breaks[,"end"])

cat(header)
header

str_split(header, "\n")

breaks <- str_locate(email[1],'\nDate: ')
email1 <- str_sub(email[1], start=breaks[,'end']+1)
breaks1 <- str_locate(email1,'\nMessage-ID:')
cat(str_sub(email1,end=breaks1[,'start']))

str_match(header, "Date: ([a-zA-Z]{3}), ([0-9]{2}) ([a-zA-Z]{3}) ([0-9]{4}) ([0-9]{2}:[0-9]{2}:[0-9]{2} -?[0-9]{4})")

str_match(header, "From: \"?([a-zA-Z]*, [a-zA-Z]*)\"? <([^>]*)")
```

```{r}
str_detect(words, "^r.*e$")
str_subset(words, "^r.*e$")
```

IRF1t <- 1
RIGIt <- 2
targets <- list(c(IRF1t, "IRF1t"),
                c(RIGIt, "RIGIt")
                )
for (target in targets) {
print(target)
}
